Reliable error estimation for Sobol' indices

### 2016-08-18 article/article.tex
added template journal and aux. files

\subsection{Definition of Sobol' indices}
%We adopt the same notations introduced by Owen in \cite{Owen}. 
Denote by $f$ a numerical model, by $\vx=(x_1,\dots,x_d)$ its vector of inputs and set $\mathcal{D}=\{1,\dots,d\}$. The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$. Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.

Let $f$ be the symbol representing the numerical model studied. We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding} of $f$:
\begin{equation}
f(\vx)=\mu+\sum \limits_{u \subseteq \mathcal{D}} f_u(\vx),
\label{anova}
\end{equation}
where:
\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
Due to orthogonality, taking the variance of each side in equation (\ref{anova}) leads to the variance decomposition of $f$:
\[ \sigma^2 = \sum \limits_{u \subseteq \{1,\dots,d\}} \sigma_v^2, \ \text{ with } \ \sigma_v^2=\int_{[0,1)^{|v|}} f_v(\vx)^2 d{\vx}.\]
From the variance decomposition of $f$, on can express the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subsetneq \mathcal{D}.\]

@@

$\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$. These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index for the set $u$.
\bigskip

The problem of interest here is the evaluation of first-order and total effect Sobol' indices. The computation of these indices is performed based on the following integral formula for their numerators:
\begin{align}
\label{first.order}
\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}, \\
\label{total.effect}
\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}, \qquad u \in \mathcal{D},
\end{align}
The variance of $f$ is evaluated by:
\[ \sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \text{ with } \ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}.\]
Most of the time, the complexity of $f$ causes the computation of $\mu$, $\sigma^2$ and integrals (\ref{first.order}) and (\ref{total.effect}) to be intractable. In such case, one needs to rely on an estimation of these quantities.

@@

One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u}\right)f(\vx'_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$ the classic estimator:
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - \widehat{\mu}^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
The estimation of a single pair ($\underline{\tau}_u^2$, $\ov{$\tau$}_u^2$) requires $3n$ evaluations of the model $f$. Using a combinatorial formalism, in \cite[Theorem 1]{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and all total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$. While elegant, this approach still requires a number of model evaluations that grows linearly with respect to the input space dimension.

An efficient alternative to evaluate all first-order indices was proposed by Mara \textit{et al.} \cite{Mara}  requiring only $2n$ model evaluations. This alternative relies on the construction of two replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}. The definition we give here introduce the structure in a wider context:
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1)^{d}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$. We note $\pi_u$ the permutation reordering the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
\end{definition}
The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in formula (\ref{first.order.est}).

More specifically, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$. Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$. Consider $u \in \mathcal{D}$, from Definition \ref{rep.designs} there exists a permutation $\pi_u$ such that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$. Then, remark that $\forall i \in \{0,\dots,n-1\}$:
\[\pi_u(f({\vx'}_i))=f({\vx'}_{\pi_u(i)})=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u})\]
%\pi_u(f({\vx'}_{i,u}:{\vx'}_{i,-u}))
Each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$ without requiring further model evaluations. This estimation method has been deeply studied and generalized in Tissot et al. \cite{Mara} to the case of closed second-order indices. In the following we refer to this method as replication procedure.
\bigskip

\subsection{Towards a reliable estimation}
The aim of this paper is to propose a recursive estimation procedure to estimate Sobol' indices. The choice of the stopping criterion is the key point of this paper.

In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure. In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps. More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates. Such stopping criteria often involved hyperparameters hard to tweak but above all fail to guarantee any error bound on the estimation. 
\bigskip

Our recursive procedure stands apart from others approaches by the construction of a robust stopping criterion. This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}). This decomposition use the close set property of digital sequences. As such, our recursive procedure relies on the iterative construction of Sobol' sequences. The iterative construction of the Sobol' sequences is performed accordingly to the multiplicative  approach presented in \cite{crass}.

The construction of the error bound is the subject of the next section \ref{section.error}. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.

\section{Reliable Error Estimation for Cubatures}
\label{section.error}

\subsection{Reliable Estimation Using Quasi-Monte Carlo}
\label{section.error.algo}

@@

As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\phi_{\vk}(\vx):=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}/b}$,
\begin{equation}\label{basis_integ_prop}
\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
\begin{cases}
1,\quad \vk\in\mathcal{P}_m^\perp, \\
0,\quad \vk\notin\mathcal{P}_m^\perp
\end{cases}
\end{equation}
Therefore, considering the Walsh decomposition $f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)$ for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
\begin{align*}
\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} & = \abs{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}\\
& = \abs{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
\end{align*}

@@

The details about the algorithm, mapping of the wavenumber space, or meaning and properties of $\cc$, are discussed in \cite{HicJim}.

\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_2}{I_3-(I_4)^2}.
\end{align*}
If $\vI:=(I_1,I_2,I_3,I_4)$, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ and error bound $\varepsilon_{\vI}$ according to \ref{section.error.algo}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.

Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we propose the following estimators:
\begin{align*}
\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right), \\
\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right),
\end{align*}
and,
\begin{align*}
\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right), \\
\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right).
\end{align*}
These new estimators allow us to say that $\underline{S}_u\in [\widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u}]$ and $\overline{S}_u\in [\widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u}]$.

For a better understanding of these estimators, we provide and example in dimension 1 below,
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{Images/scheme_S.eps}
\end{figure}

@@

The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}, namely Saltelli's strategy and the replication procedure. The form of the stopping criterion is the same for both strategies. It is defined as $\abs{\varepsilon_{S_u}} \leq \epsilon$, where $\epsilon$ is the desired precision on the Sobol' indices.

We start be detailing our recursive procedure in the form of an algorithm. Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for first-order indices.

@@

Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure. First, fix the target precision $\epsilon >0$. Set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}. With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences. Furthermore, they possess the structure of two replicated designs of order $1$.
\bigskip

$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices. This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}. Or $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices. This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.

>>>>

\subsection{Definition of Sobol' indices}
%We adopt the same notations introduced by Owen in \cite{Owen}. 
Denote by $f$ a numerical model, by $\vx=(x_1,\dots,x_d)$ its vector of inputs and set $\mathcal{D}=\{1,\dots,d\}$. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.

Let $f$ be the symbol representing the numerical model studied. We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding} of $f$:
\begin{equation}
f(\vx)=\mu+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
Due to orthogonality, taking the variance of each side in equation (\ref{anova}) leads to the variance decomposition of $f$:
\[ \sigma^2 = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From the variance decomposition of $f$, on can express the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subsetneq \mathcal{D}.\]

@@

$\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$. These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index.
\bigskip

The problem of interest here is the evaluation of first-order and total effect Sobol' indices. The computation of these indices is performed based on the following integral formulas for their numerators:
\begin{align}
\label{first.order}
\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'_{-u}}, \\
\label{total.effect}
\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d{\vx'} d\vx_u, \qquad u \in \mathcal{D},
\end{align}
The variance of $f$ is evaluated by:
\begin{equation}
\sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \text{ with } \ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}.
\label{eq.sigma.mu}
\end{equation} 
Most of the time, the complexity of $f$ causes the computation of integrals (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable. In such case, one needs to rely on an estimation of these quantities.

@@

One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u}\right)f(\vx'_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$ the classic estimator:
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - \widehat{\mu}^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
The Sobol' indices estimators are defined by:
\begin{equation*}
\widehat{\underline{S}_u} = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}_u} = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\end{equation*}
The estimation of a single pair ($\widehat{\underline{S}_u}$, $\widehat{\overline{S}_u}$) requires $3n$ evaluations of the model $f$. Using a combinatorial formalism, in \cite[Theorem 1]{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and all total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$. While elegant, this approach still requires a number of model evaluations that grows linearly with respect to the input space dimension.

An efficient alternative to evaluate all first-order indices was proposed by Mara \textit{et al.} \cite{Mara}  requiring only $2n$ model evaluations. This alternative relies on the construction of two replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}. The definition we give here introduce the structure in a wider context:
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1)^{d}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$. We note $\pi_u$ the permutation arranging the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
\end{definition}
The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in formula (\ref{first.order.est}).

More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$. Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$. Consider $u \in \mathcal{D}$, from Definition \ref{rep.designs} there exists a permutation $\pi_u$ such that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$. Then, remark that $\forall i \in \{0,\dots,n-1\}$:
\[\pi_u(f({\vx'}_i))=f({\vx'}_{\pi_u(i)})=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).\]
Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$ without requiring further model evaluations. This estimation method has been deeply studied and generalized in Tissot et al. \cite{Mara} to the case of closed second-order indices. In the following we refer to this method as replication procedure.

\subsection{Towards a reliable estimation}
The aim of this paper is to propose a recursive procedure to estimate first-order and total effect Sobol' indices. The choice of the stopping criterion is the key point of this paper. In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure. In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps.

More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates. Such stopping criteria often involve hyper-parameters hard to tweak but above all fail to guarantee any error bound on the estimates. 
\bigskip

Our recursive procedure stands apart from others approaches with the construction of a robust stopping criterion. This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}). This decomposition use the close set property of digital sequences. As such, our recursive procedure relies on an iterative construction of Sobol' sequences. This construction is performed accordingly to the multiplicative  approach presented in \cite{crass}.

The construction of the error bound is the subject of the next section. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.

\section{Reliable error bound for Sobol' indices}
\label{section.error}

\subsection{Reliable integral estimation using quasi-Monte Carlo}
\label{section.error.algo}

@@

As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\phi_{\vk}(\vx)$,
\begin{equation}\label{basis_integ_prop}
\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
\begin{cases}
1,\quad \vk\in\mathcal{P}_m^\perp, \\
0,\quad \vk\notin\mathcal{P}_m^\perp
\end{cases}
\end{equation}
Therefore, considering the Walsh decomposition $f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)$ for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
\begin{align*}
\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} & = \abs{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}\\
& = \abs{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
\end{align*}

@@

Details concerning the algorithm, mapping of the wavenumber space, or meaning and properties of $\cc$, are provided in \cite{HicJim}. For the rest of the paper we only consider Sobol' sequences. These sequences are digital sequences in based $b=2$. Their major interests come from their fast and easy implementation as well as their slow growing size rate. Further details concerning these sequences can be found in \cite{Lemieuxbook,Niederreiter92}.

\subsection{Generalization to Sobol' indices}
The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,

\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2} = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2} = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
where $\vI=(I_1,I_2,I_3,I_4)$. Thus, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ and error bound $\varepsilon_{\vI}$ according to \ref{section.error.algo}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
\bigskip

Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we consider here the following estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right), \\
\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right),
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right), \\
\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right).
\end{aligned}
\label{formula_oversu}
\end{gather}
These new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] ;\] This property is illustrated below in dimension one.   
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Images/scheme_S.eps}
\end{figure}

@@

The recursive estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}, namely Saltelli's strategy and the replication procedure.

We start be detailing our recursive procedure in the form of an algorithm. Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for the first-order indices.

@@

Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure. First, one must fix the target precision $\epsilon >0$ for the Sobol' estimates. The stopping criterion is initialized with $\zeta=\epsilon+1$. Then, we set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}. With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences. Furthermore, they possess the structure of two replicated designs of order $1$ (Definition \ref{rep.designs}).
\bigskip

$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices. This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}.

Alternatively, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices. This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
